HPC--101\\Onboarding

### 2016-03-02 hpc_101/paper.tex
update to slides. moved x11 to aux sectio.  swtiched to --memn

\begin{frame}
\frametitle{SLURM commands}\footnotesize
SLURM has a series of commands, each of which allow users to interact with the job scheduler
\begin{itemize}\tiny
	\item \emph{\textbf{srun}} --  Used to submit a job for execution or initiate job steps in real time
	\item \emph{\textbf{srun.x11}} -- Used to submit an interactive job with X11 support
	\item \emph{\textbf{sbatch}} -- Used to submit a job script for later execution. The script could contain one or more srun commands
	\item \emph{\textbf{scancel}} -- Used to cancel a pending or running job or job step. It can also be used to send an arbitrary signal to all processes associated with a running job or job step
	\item \emph{\textbf{sinfo}} -- Reports the state of partitions and nodes managed by Slurm. It has a wide variety of filtering, sorting, and formatting options
	\item \emph{\textbf{squeue}} -- Reports the state of jobs or job steps
	\item \emph{\textbf{sacct}} -- Used to report job or job step accounting information about active or completed jobs
	\item \emph{\textbf{scontrol}} -- The administrative tool used to view and/or modify Slurm state. Note that many scontrol commands can only be executed as user root
\end{itemize}
\begin{itemize}
	\item[--] Examples usage of the SLURM commands can be seen on schedmd's \href{http://slurm.schedmd.com/quickstart.html}{quickstart}
	\item[--] Each command should have a `man' page, or displays help when the -h flag is used
\end{itemize}
\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session (no X11)}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00 \ddash{}pty /bin/bash
          ~\\
          ~\\
          \hrule
          ~\\
	$[$login \ctilde$]$\$ srun -I -p sb.q -N 1 -c 1 -n 1 -t 0-01:00:00 \ddash{}pty /bin/bash

	\end{block}

	\begin{block}{Interactive session (with X11)}\tiny
		\begin{enumerate}
			\item Connect via SSH using the -Y option, X11 forwarding enabled
			\item run srun.x11 to start a session on a node
		\end{enumerate}
		~\\
		~\\
		$[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
		$[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
		$[$compute-0001 \ctilde$]$\$ xterm	~\\
	\end{block}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                             
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid.
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid.
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                              
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid.
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid.
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                               
\#SBATCH \ddash{}error=buzz-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=buzz-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 90 days.
\begin{itemize}
 \item Which of my directories are subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} All files and folders found in \ctilde/lus/ are subject to the 90 day purge policy.  Symlinks are excluded from the purge, and are not followed by the purge bot.  
   \end{itemize}
\item How frequently are files for purging identified?
   \begin{itemize}
   \item \textbf{Answer:} Current frequency is every other month, but the frequency many increase or decrease based on the fill rate of the {\lustre} filesystem 
	\end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

@@

>>>>

\begin{frame}
\frametitle{SLURM commands}\footnotesize
SLURM has a series of commands, each of which allow users to interact with the job scheduler
\begin{itemize}\tiny
	\item \emph{\textbf{srun}} --  Used to submit a job for execution or initiate job steps in real time
	\item \emph{\textbf{sbatch}} -- Used to submit a job script for later execution. The script could contain one or more srun commands
	\item \emph{\textbf{squeue}} -- Reports the state of jobs or job steps
	\item \emph{\textbf{scancel}} -- Used to cancel a pending or running job or job step. It can also be used to send an arbitrary signal to all processes associated with a running job or job step
	\item \emph{\textbf{sinfo}} -- Reports the state of partitions and nodes managed by Slurm. It has a wide variety of filtering, sorting, and formatting options
	\item \emph{\textbf{sacct}} -- Used to report job or job step accounting information about active or completed jobs
	\item \emph{\textbf{scontrol}} -- The administrative tool used to view and/or modify Slurm state. Note that many scontrol commands can only be executed as user root
\end{itemize}
\begin{itemize}
	\item[--] Examples usage of the SLURM commands can be seen on schedmd's \href{http://slurm.schedmd.com/quickstart.html}{quickstart}
	\item[--] Each command should have a `man' page, or displays help when the -h flag is used
\end{itemize}
\numlessfootnotetxt{\tiny \url{http://slurm.schedmd.com/quickstart.html}}
\end{frame}

@@

\subsection{Interactive Job -- srun}
\frametitle{SLURM Job Scripts}
\begin{frame}
\frametitle{Interactive Job with SLURM}
	\begin{block}{Interactive session}\tiny
	$[$login \ctilde$]$\$ srun \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00 \ddash{}pty /bin/bash
          ~\\
          ~\\
          \hrule
          ~\\
	$[$login \ctilde$]$\$ srun -I -p sb.q -N 1 -c 1 -n 1 -t 0-01:00:00 \ddash{}pty /bin/bash

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=hello-\%A.err \#\# \%A - filled with jobid
\#SBATCH \ddash{}output=hello-\%A.out \#\# \%A - filled with jobid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\#!/bin/bash
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem=11000 \#\# max amount of memory per node you require
\#SBATCH \ddash{}error=buzz-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=buzz-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 90 days.
\begin{itemize}
 \item Which of my directories are subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} All files and folders found in \ctilde/lus/ are subject to the 90 day purge policy.  Symlinks are excluded from the purge, and are not followed by the purge bot.  
   \end{itemize}
\item How frequently are files for purging identified?
   \begin{itemize}
   \item \textbf{Answer:} Taking into account the fill rate of the {\lustre} filesystem, a purge is performend as usage approaches 80\%.
   \end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

@@

\begin{frame}	
\frametitle{FAQ}
\begin{itemize}
  \item Can I run a display program on the cluster?
    \begin{itemize}
      \item \textbf{Answer:} Yes, but not from the login nodes.  To follow cluster usage policies, please run X11 applications from a compute node.  Please see the following steps.
\end{itemize}
\end{itemize}
 \begin{block}{Interactive session with X11}\tiny  
       \begin{enumerate}
      \item Connect via SSH using the -Y option, X11 forwarding enabled
      \item run srun.x11 to start a session on a node
      \end{enumerate}
      \
      ~\\
      ~\\
      $[$local \ctilde$]$\$ ssh -Y user99@uhhpc1.its.hawaii.edu	~\\
      $[$login \ctilde$]$\$ srun.x11 \ddash{}immediate \ddash{}partition sb.q \ddash{}nodes 1 \ddash{}cpus-per-task 1 \ddash{}tasks-per-node 1 \ddash{}time 0-01:00:00	~\\
      $[$compute-0001 \ctilde$]$\$ xterm	~\\
 \end{block}
